What We Eval in the Shadows

### 2021-08-06 paper/main.tex
authors

\documentclass[review,screen,acmsmall,anonymous=true]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

@@

\author{Author }
\authornote{Both authors contributed equally to this research.}
\email{a@b.com}\orcid{}\author{Author}\authornotemark[1]
\email{r@s.com}
\affiliation{\institution{Institute} \country{Country}}

>>>>

\documentclass[review,screen,acmsmall]{acmart}
%\settopmatter{printfolios=false,printccs=false,printacmref=false}
\setcopyright{none}
\renewcommand\footnotetextcopyrightpermission[1]{}
\pagestyle{plain}

@@

\author{Pierre Donat-Bouillud}\affiliation{\institution{Czech Technical University in Prague}\country{Czech Republic}}
\author{Aviral Goel}\affiliation{\institution{Northeastern University}\country{USA}}
\author{Filip Křikava}\affiliation{\institution{Czech Technical University in Prague}\country{Czech Republic}}
\author{Christoph Kirsch}\affiliation{\institution{Czech Technical University in Prague}\country{Czech Republic}}
\author{Jan Vitek}\affiliation{\institution{Northeastern University}\country{USA}}
\affiliation{\institution{Czech Technical University in Prague}\country{Czech Republic}}
